---
title: "LabExercise2"
output: word_document
date: "2024-02-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
50 Products Scraped

product_1
Osprey Europe Talon 11 Men's Hiking Pack Cosmic Red
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_1 <- data.frame()

for (page in 1:5) {
  url1 <- paste0("https://www.amazon.co.uk/Osprey-Europe-Talon-Hiking-Cosmic/product-reviews/B08LPWFBW5/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session1 <- bow(url1, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session1) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Osprey Europe Talon 11 Men's Hiking Pack Cosmic Red - L/XL"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_1 <- rbind(product_1, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(product_1)


```


2ndporduct
Vans Alumni backpack Unisex children's backpack


```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_2 <- data.frame()

for (page in 1:5) {
 url2 <- paste0("https://www.amazon.co.uk/Vans-Unisex-Backpack-ALUMNI-BACKPACK/product-reviews/B0B1VPCWZS/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session2 <- bow(url2, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session2) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Vans Alumni backpack Unisex children's backpack (pack of 1), 40.5 x 29 x 19 cm"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_2 <- rbind(product_2, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

 
}

View(product_2)

```

3rdproduct


```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_3 <- data.frame()

for (page in 1:5) {
  url3 <- paste0("https://www.amazon.co.uk/JanSport-SuperBreak-Large-Backpack-Graphite/product-reviews/B0B1V81NL2/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session3 <- bow(link3, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session3) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JanSport SuperBreak One, Large Backpack, 25 L, 42 x 33 x 21 cm, Graphite Grey"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_3 <- rbind(product_3, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(product_3)
```


4thproduct
JANSPORT Unisex Big Student Bookbag with 15-Inch Laptop Compartment (pack of 1)

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_4 <- data.frame()

for (page in 1:5) {
  url4 <- paste0("https://www.amazon.co.uk/JanSport-Big-Student-Backpack-Sustainable/product-reviews/B07K74LDC6/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session4 <- bow(url4, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session4) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JANSPORT Unisex Big Student Bookbag with 15-Inch Laptop Compartment (pack of 1)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_4 <- rbind(product_4, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))
}

View(product_4)

```
5thprodcut

JanSport Big Student, Large Backpack, 51 L, 43 x 33 x 25 cm, 15in laptop compartment, Blue Neon"

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_5 <- data.frame()

for (page in 1:5) {
  url5 <- paste0("https://www.amazon.co.uk/JanSport-Student-Backpack-laptop-compartment/product-reviews/B0C6KMTDKG/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session5 <- bow(url5, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session5) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JanSport Big Student, Large Backpack, 51 L, 43 x 33 x 25 cm, 15in laptop compartment, Blue Neon"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_5 <- rbind(product_5, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(product_5)
```
6thproduct

JanSport SuperBreak One, Large Backpack
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_6 <- data.frame()

for (page in 1:5) {
  url6 <- paste0("https://www.amazon.co.uk/JanSport-SuperBreak-Backpack-Screen-Static/product-reviews/B0C6KK5S75/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session6 <- bow(url6, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session6) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }
  
  productName <- "JanSport SuperBreak One, Large Backpack, 47 L, 42 x 33 x 21 cm, Screen Static"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_6 <- rbind(product_6, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(product_6)

```

7thproduct
Jansport SuperBreak Backpack
```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_7 <- data.frame()

for (page in 1:5) {
  url7 <- paste0("https://www.amazon.co.uk/JANSPORT-Superbreak-Backpack-Jansport-SuperBreak/product-reviews/B0007QCQGI/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session7 <- bow(url7, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session7) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Jansport SuperBreak Backpack"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_7 <- rbind(product_7, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(product_7)

```


8thproduct
JANSPORT Unisex Cortlandt Everyday Advanture Tech Backpack (pack of 1)
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_8 <- data.frame()

for (page in 1:5) {
  url8 <- paste0("https://www.amazon.co.uk/JanSport-Cortlandt-Backpack-Laptop-Compartment/product-reviews/B0B1V6GBPP/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session8 <- bow(url8, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session8) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JANSPORT Unisex Cortlandt Everyday Advanture Tech Backpack (pack of 1)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_8 <- rbind(product_8, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  Sys.sleep(3)
}

View(product_8)
```
9thproduct
Vans Unisex Alumni Pack 5 Backpack (pack of 1)

```{r}

library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_9 <- data.frame()

for (page in 1:5) {
  url9 <- paste0("https://www.amazon.co.uk/Vans-Unisex-Backpack-ALUMNI-ROYALE-WHITE/product-reviews/B0B1VSJ3QM/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session9 <- bow(url9, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session9) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "Vans Unisex Alumni Pack 5 Backpack (pack of 1)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_9 <- rbind(product_9, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

}

View(product_9)


```
10thproduct
JanSport SuperBreak One, Large Backpack, 46 L, 42 x 33 x 21 cm, Precious Petal s

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_10 <- data.frame()

for (page in 1:5) {
  url10 <- paste0("https://www.amazon.co.uk/JanSport-SuperBreak-Backpack-Precious-Petals/product-reviews/B0C6KKXCW1/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session10 <- bow(url10, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session10) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JanSport SuperBreak One, Large Backpack, 46 L, 42 x 33 x 21 cm, Precious Petals"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_10 <- rbind(product_10, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(product_10)
```

11thproduct
JANSPORT Men's Superbreak 100% Nylon Bags

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_11 <- data.frame()

for (page in 1:2) {
  url11 <- paste0("https://www.amazon.co.uk/Jansport-Superbreak-Pink-100-Nylon/product-reviews/B07D438MM5/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session11 <- bow(url11, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session11) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JANSPORT Men's Superbreak 100% Nylon Bags"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:50]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:50]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:50]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:50]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:50]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:50]

  product_11 <- rbind(product_11, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(product_11)
```
12thproduct
JANSPORT Big Student, Large Backpack, Red Tape, 34 L, 43 x 33 x 25 cm, 15 in laptop compartment
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_12 <- data.frame()

for (page in 1:2) {
  url12 <- paste0("https://www.amazon.co.uk/Jansport-Big-Student-Backpack-Tape/product-reviews/B08YRVTWW6/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session12 <- bow(url12, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session12) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JANSPORT Big Student, Large Backpack, Red Tape, 34 L, 43 x 33 x 25 cm, 15 in laptop compartment"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_12 <- rbind(product_12, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

 
}

View(product_12)
```
13thproduct
JanSport Cool Student
```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_13 <- data.frame()

for (page in 1:5) {
  url13 <- paste0("https://www.amazon.co.uk/JANSPORT-JS0A47JK-JanSport-Student-Backpack/product-reviews/B07PKVX44C/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session13 <- bow(url13, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session13) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JanSport Cool Student"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_13 <- rbind(product_13, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

  
}

View(product_13)
```
14thproduct

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_14 <- data.frame()

for (page in 3:7) {
  url14<- paste0("https://www.amazon.co.uk/JanSport-Big-Student-Backpack-Sustainable/product-reviews/B07K74LDC6/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session14 <- bow(url14, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session14) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "JANSPORT Unisex Big Student Bookbag with 15-Inch Laptop Compartment (pack of 1)"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_14 <- rbind(product_14, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))

 
}

View(product_14)
```


15thproduct
KROSER School Laptop Backpack 17.3 Inch Large Travel Computer Backpack Water-Repellent Daypack with USB Charging Port & Headphone Interface RFID Pockets for Work/Business/College/Men/Women

```{r}
library(dplyr)
library(rvest)
library(polite)
library(httr)
library(selectr)

product_15 <- data.frame()

for (page in 1:5) {
url15 <- paste0("https://www.amazon.co.uk/KROSER-15-6-17-3-Water-Repellent-Headphone-Interface/product-reviews/B07MK6JZ9S/ref=cm_cr_dp_d_show_all_btm_next_", page, "?ie=UTF8&reviewerType=all_reviews&pageNumber=", page)
  session15 <- bow(url15, user_agent = "Educational Purpose")

  scrapeNodes <- function(selector) {
    scrape(session15) %>%
      html_nodes(selector) %>%
      html_text(trim = TRUE)
  }

  productName <- "KROSER School Laptop Backpack 17.3 Inch Large Travel Computer Backpack Water-Repellent Daypack with USB Charging Port & Headphone Interface RFID Pockets for Work/Business/College/Men/Women"
  scrapedTitle <- scrapeNodes("span.a-size-base.review-title.a-color-base.review-title-content.a-text-bold")[1:10]
  scrapedReviewer <- scrapeNodes("span.a-profile-name")[1:10]
  scrapedReview <- scrapeNodes("span.a-size-base.review-text.review-text-content")[1:10]
  scrapedDate <- scrapeNodes("span.a-size-base.a-color-secondary.review-date")[1:10]
  scrapedRating <- scrapeNodes("span.a-icon-alt")[1:10]
  scrapedType <- scrapeNodes("span.a-size-mini.a-color-state.a-text-bold")[1:10]

  product_15 <- rbind(product_15, data.frame(
    prod_name = productName,
    title = scrapedTitle,
    reviewer = scrapedReviewer,
    review = scrapedReview,
    date = scrapedDate,
    ratings = scrapedRating,
    type_of_purchase = scrapedType
  ))


}

View(product_15)
```
